### 2017-11-29 manuscript.rmd
merged results & discussion - expanded phylogeny discussion

## Results

### Species phylogeny and hypothesis testing

Specimens were collected in the eastern Pacific Ocean, Mediterranean, and the Gulf of California (table 1). All sequence data have been deposited in the sequence read archive (SRA). The analyses presented here consider 34 siphonophore species and 9 outgroup species. This includes new data for 30 species. Summary statistics for expression libaries are given in supplementary table x. In the final analyses, we sampled 1,071 genes to generate a supermatrix with 60% occupancy and a length of 378,468 amino acids (gene occupancy matrix - supplementary figure 1). 
```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

@@

```
These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (figure 3) [@Dunn:2005dy]. Cystonectae is the sister group to the remaining siphonophores, Calycophorae is nested within the paraphyletic "Physonectae", and *Apolemia* is sister to all other Codonophora. In addition, multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. *Physophora gilmeri*, along with *Lychnagalma utricularia* (not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*. *Cordagalma cordiforme* was previously unresolved, while in this analysis *Cordagalma sp* falls within the Agalmatidae.  Additionally, there is strong support for *Bargmannia* as sister to all non-Apolemid codonophorans.

@@

These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) [@Dunn:2005dy]. Cystonectae is the sister group to the remaining siphonophores, Calycophorae is nested within the paraphyletic "Physonectae", and *Apolemia* is sister to all other Codonophora. In addition, multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. *Physophora gilmeri*, along with *Lychnagalma utricularia* (not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*. *Cordagalma cordiforme* was previously unresolved, while in this analysis *Cordagalma sp* falls within the Agalmatidae.  Additionally, there is strong support for *Bargmannia* as sister to all non-Apolemid codonophorans.

@@

##Discussion

###Siphonophore Phylogeny

@@

In our previous siphonophore phylogenetic analysis [@Dunn:2005dy] there were several characters left with equivocal evolutionary histories, due to unresolved relationships between physonects. With our current cladistic resolution, we were able to answer some of the questions left open:

@@

![Stochastic mapping reconstruction of the evolutionary history of A) palpon zooids, and B) distribution of sexual zooids on the colonies. The color gradients shows the reconstructed probability estimate of the discrete character states along the branches.](figures/Figure5.pdf)

>>>>

## Results and Discussion

### Species phylogeny and hypothesis testing
Specimens were collected in the eastern Pacific Ocean, Mediterranean, and the Gulf of California (table 1). All sequence data have been deposited in the sequence read archive (SRA). The analyses presented here consider 34 siphonophore species and 9 outgroup species. This includes new data for 30 species. Summary statistics for expression libaries are given in supplementary table x. In the final analyses, we sampled 1,071 genes to generate a supermatrix with 60% occupancy and a length of 378,468 amino acids (gene occupancy matrix - supplementary figure 1). 
```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

@@

```
These findings are largely consistent with a previous analysis based on two genes (16S and 18S ribosomal RNA) (figure 3) [@Dunn:2005dy]. There is strong support for the Cystonectae as sister to all other siphonophores, the Codonophora. We also find strong support for Calycophorae nested within the paraphyletic "Physonectae", and for the Apolemidae as sister to all other Codonophora. Multiple nodes that were not resolved in the previous two-gene analysis do recieve strong support in this 1,071-gene transcriptome analysis. There is strong support for the Pyrostephidae as sister to all non-Apolemid codonophorans. Within the clade that is sister to the Pyrostephidae, we find two main clades, the Calycophorae and a clade we call the Euphysonectae, which includes the remaining non-Apolemid, non-Pyrostephid historically recognized Physonectae. Given the relatively shallow sampling of this analysis, we define the Euphysonectae as the clade consisting of *Agalma elegans* and all taxa that are more closely related to it than to the Calycophorae.

In this phylogeny, *Physophora gilmeri* along with *Lychnagalma utricularia* (both not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*, a clade restricted to *Agalma*, the Athorybiidae,*Halistemma* and *Nanomia* [@Dunn:2005dy]. In the rDNA study, *Physophora hydrostatica* was sister to the Forskaliidae with low support. *Cordagalma cordiforme* (= *Cordagalma ordinatum* [@pugh2016synopsis]) was previously unresolved, while in this analysis *Cordagalma* sp is in a clade with *Forskalia asymmetrica*, falling outside of the Agalmatidae *sensu stricto*. *Cordagalma* has traditionally been placed within the Agalmatidae *sensu lato* [@totton1965synopsis], although the Agalmatidae is considered to be a catch-all family in need of revision [@pugh2006taxonomic,@pugh1998re, @Dunn:2005dy]. Within the calycophorans, taxon sampling is shallower, however there is broad agreement with the previous analysis. *Craseoa lathetica* and *Desmophyes haematogaster* are sister to *Hippopodius hippopus*

@@

@@

@@

@@

![Stochastic mapping reconstruction of the evolutionary history of A) palpon zooids, and B) distribution of sexual zooids on the colonies. The color gradients show the reconstructed probability estimate of the discrete character states along the branches.](figures/Figure5.pdf)
